Supporting Information for\\ ``A weakly structured stem for human origins in Africa''

### 2022-07-27 supplement.tex
ADRP throughout

The IICR is only a reliable estimator of $N_e$ in the absence of population structure.
However, since IIRC are readily estimated and visually interesting,
it is commonly attempted even when the assumption is not met.
Even if the assumption is not met, the inferred IIRC can be interpreted as a
summary statistic for which model predictions can be compared to data.
It can therefore be
informative about aspects of the data that our models fail to predict.
We also note that the coalescence rates inferred from data used a larger set of
populations from the combined 1000 Genomes/AGRP dataset, while our model
simulations only included a subset of 5 populations. This may lead to
differences in resolution of the inferences.

@@

\begin{figure}[ht]
    \centering
    \includegraphics{figures/supp-relate-iicr-data}
    \caption{
        \textbf{Inverse instantaneous coalescence rates inferred from the data.}
        Using combined data from the Thousand Genomes Project and the AGRP,
        we reconstructed gene genealogies using Relate and calculated the
        inverse instantaneous coalescence rate for samples within each population.
        (A) Eurasian populations (CEU: European American, GBR: British,
        CHB: Han Chinese, PJL: Punjabi), (B) Thousand Genomes African populations
        (ACB: Afro-Caribbean, ASW: African American, ESN: Esan, GWD: Gambian,
        LWK: Luhya, MSL: Mende, YRI: Yoruba), (C) AGRP populations.
    }
    \label{fig:supp-iicr-data}
\end{figure}

>>>>

The IICR is only a reliable estimator of $N_e$ in the absence of population structure.
However, since IIRC are readily estimated and visually interesting,
it is commonly attempted even when the assumption is not met.
Even if the assumption is not met, the inferred IIRC can be interpreted as a
summary statistic for which model predictions can be compared to data.
It can therefore be
informative about aspects of the data that our models fail to predict.
We also note that the coalescence rates inferred from data used a larger set of
populations from the combined 1000 Genomes/ADRP dataset, while our model
simulations only included a subset of 5 populations. This may lead to
differences in resolution of the inferences.

@@

\begin{figure}[ht]
    \centering
    \includegraphics{figures/supp-relate-iicr-data}
    \caption{
        \textbf{Inverse instantaneous coalescence rates inferred from the data.}
        Using combined data from the Thousand Genomes Project and the ADRP,
        we reconstructed gene genealogies using Relate and calculated the
        inverse instantaneous coalescence rate for samples within each population.
        (A) Eurasian populations (CEU: European American, GBR: British,
        CHB: Han Chinese, PJL: Punjabi), (B) Thousand Genomes African populations
        (ACB: Afro-Caribbean, ASW: African American, ESN: Esan, GWD: Gambian,
        LWK: Luhya, MSL: Mende, YRI: Yoruba), (C) ADRP populations.
    }
    \label{fig:supp-iicr-data}
\end{figure}
